Lineage Analysis of CRISPR and shRNA Screens

### 2018-08-21 lineages_18Q3.Rmd
update CRISPR heatmap code

Heatmap code:
```{r, eval=FALSE}
chm_scores_plot <- Heatmap(chm_scores, name = "CERES Score",
        bottom_annotation = HeatmapAnnotation(df = chm_annot),
        bottom_annotation_height = unit(5, "in"),
        row_title = "Genes", column_title = "Cancer Cell Lines (Broad IDs)",
        col = colorRamp2(c(-15, 0, 5), c("purple4", "white", "seagreen4")),
        na_col = "black",
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        show_column_names = FALSE,
        row_title_gp = gpar(fontsize = 60, fontface = "bold"),
        show_row_names = FALSE,
        row_dend_reorder = TRUE,
        column_dend_reorder = TRUE,
        clustering_distance_rows = "euclidean",
        clustering_distance_columns = "euclidean",
        clustering_method_rows = "complete",
        clustering_method_columns = "complete",
        column_dend_height = unit(4, "in"),
        row_dend_width = unit(4, "in"),
        width = 3)
chm_ge_plot <- Heatmap(chm_ge, name = "Gene Expression (RPKM)",
        cluster_rows = FALSE, cluster_columns = FALSE,
        show_row_names = FALSE, show_column_names = FALSE,
        column_title = "Gene Expression",
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        column_order = colnames(chm_scores)[unlist(column_order(chm_scores_plot))],
        row_order = rownames(chm_scores)[unlist(row_order(chm_scores_plot))],
        width = 1)
chm_cn_plot <- Heatmap(chm_cn, name = "Copy Number",
        cluster_rows = FALSE, cluster_columns = FALSE,
        show_row_names = FALSE, show_column_names = FALSE,
        column_title = "Copy Number",
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        column_order = colnames(chm_scores)[unlist(column_order(chm_scores_plot))],
        row_order = rownames(chm_scores)[unlist(row_order(chm_scores_plot))],
        width = 1)
chm_mut_plot <- Heatmap(chm_mut, name = "Mutation Status",
        col = c("cyan3", "darkorchid"),
        cluster_rows = FALSE, cluster_columns = FALSE,
        show_row_names = FALSE, show_column_names = FALSE,
        column_title = "Mutation Status",
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        column_order = colnames(chm_scores)[unlist(column_order(chm_scores_plot))],
        row_order = rownames(chm_scores)[unlist(row_order(chm_scores_plot))],
        width = 1)

chm_all_plot <- chm_scores_plot + chm_ge_plot + chm_cn_plot + chm_mut_plot

pdf("./plots_18Q3/crispr_heatmap_all.pdf", width = 100, height = 100, paper = "special") 
draw(chm_all_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
dev.off()
```

>>>>

Heatmap code:
```{r, eval=TRUE}
chm_scores_plot <- Heatmap(chm_scores, name = "CERES Score",
        bottom_annotation = HeatmapAnnotation(df = chm_annot),
        bottom_annotation_height = unit(5, "in"),
        row_title = "Genes", column_title = "Cancer Cell Lines (Broad IDs)",
        col = colorRamp2(c(-15, 0, 5), c("purple4", "white", "seagreen4")),
        na_col = "black",
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        show_column_names = FALSE,
        row_title_gp = gpar(fontsize = 60, fontface = "bold"),
        show_row_names = FALSE,
        row_dend_reorder = TRUE,
        column_dend_reorder = TRUE,
        clustering_distance_rows = "euclidean",
        clustering_distance_columns = "euclidean",
        clustering_method_rows = "complete",
        clustering_method_columns = "complete",
        column_dend_height = unit(4, "in"),
        row_dend_width = unit(4, "in"),
        width = 3)

chm_plot_cols <- colnames(chm_scores)[unlist(column_order(chm_scores_plot))]
chm_plot_rows <- rownames(chm_scores)[unlist(row_order(chm_scores_plot))]

chm_ge_plot <- Heatmap(chm_ge, name = "Gene Expression (RPKM)",
        na_col = "black",
        cluster_rows = FALSE, cluster_columns = FALSE,
        show_row_names = FALSE, show_column_names = FALSE,
        column_title = "Gene Expression",
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        column_order = chm_plot_cols,
        row_order = chm_plot_rows,
        width = 1)
chm_cn_plot <- Heatmap(chm_cn, name = "Copy Number",
        na_col = "black",
        cluster_rows = FALSE, cluster_columns = FALSE,
        show_row_names = FALSE, show_column_names = FALSE,
        column_title = "Copy Number",
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        column_order = chm_plot_cols,
        row_order = chm_plot_rows,
        width = 1)
chm_mut_plot <- Heatmap(chm_mut, name = "Mutation Status",
        na_col = "black",
        col = c("cyan3", "darkorchid"),
        cluster_rows = FALSE, cluster_columns = FALSE,
        show_row_names = FALSE, show_column_names = FALSE,
        column_title = "Mutation Status",
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        column_order = chm_plot_cols,
        row_order = chm_plot_rows,
        width = 1)

# chm_all_plot <- chm_scores_plot + chm_ge_plot + chm_cn_plot + chm_mut_plot
#   
# pdf("./../crispr_lineages_giant_files/crispr_heatmap_all.pdf", width = 100, height = 100, paper = "special") 
# draw(chm_all_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
# seekViewport("annotation_Cell_Line_SSMD")
# grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
# seekViewport("annotation_Cas9_Activity")
# grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
# seekViewport("annotation_Culture_Type")
# grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
# seekViewport("annotation_Primary_Tissue")
# grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
# seekViewport("annotation_Primary_Disease")
# grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
# seekViewport("annotation_Gender")
# grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
# seekViewport("annotation_Source")
# grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
# dev.off()

# pdf("./../crispr_lineages_giant_files/crispr_heatmap_ge.pdf", width = 100, height = 100, paper = "special") 
# draw(chm_scores_plot + chm_ge_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
# seekViewport("annotation_Cell_Line_SSMD")
# grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
# seekViewport("annotation_Cas9_Activity")
# grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
# seekViewport("annotation_Culture_Type")
# grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
# seekViewport("annotation_Primary_Tissue")
# grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
# seekViewport("annotation_Primary_Disease")
# grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
# seekViewport("annotation_Gender")
# grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
# seekViewport("annotation_Source")
# grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
# dev.off()

pdf("./../crispr_lineages_giant_files/crispr_heatmap_mut.pdf", width = 100, height = 100, paper = "special") 
draw(chm_scores_plot + chm_mut_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
dev.off()

pdf("./../crispr_lineages_giant_files/crispr_heatmap_cn.pdf", width = 100, height = 100, paper = "special") 
draw(chm_scores_plot + chm_cn_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
dev.off()
```
